Meta-analysis

### 2019-08-07 05_MetaAnalysis.Rmd
added analysis after removing outlier trial.

# grain yeild is not a significant predictor for yeild error (t value = -1.613)
#  And the variance decreases as the mean increases, counter to expectation
# does log transformation improve the model

PM_MB_trianLMER.1 <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
         (1|Trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER.1) # grain yeild is not a significant predictor of log(yeild error)
anova(PM_MB_trianLMER, PM_MB_trianLMER.1) # no significant difference between the models

@@

paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept to predict Yield error

lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables
dim(lmer.coef$Trial_ref)

@@

@@

PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"

Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha.` is set as a random slope to the random intercept `Trial_ref`.  
The model fits better as shown by an anova comparison. But now to determine how to impute from this model ....
```{r random_slope_model}

>>>>

# grain yeild (in this model) IS a significant predictor for yeild error (t value = 5.826)
#  And the variance increases as the mean increases
# does log transformation improve the model?

PM_MB_trianLMER.1 <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
         (1|Trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER.1) # grain yeild a significant predictor of log(yeild error)
anova(PM_MB_trianLMER, PM_MB_trianLMER.1) # no significant difference between the models

@@

# Extract the model cooeficients
paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept to predict Yield error
lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables

@@

```
```{r na2Sv_formula}

@@

PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
}

Lets look at the model without the trial mung1718/01, as it looks to be adding some skew.
```{r lmer_remove_mung1718-01}
# remove from mung1718/01 from training dataset
PM_MB_train.2 <- PM_MB_train[PM_MB_train$Trial_ref != "mung1718/01",]

# Rerun the model
PM_MB_trianLMER.5 <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
         (1|Trial_ref), data = PM_MB_train.2)
summary(PM_MB_trianLMER.5) # no significant effect of mean grain yield on yeild error

# Extract the cooeficients
paramA <- (summary(PM_MB_trianLMER.5)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
InterC <- (summary(PM_MB_trianLMER.5)$coef)[1,1] # Extract the overall mean intercept to predict Yield error
lmer.coef <- coef(PM_MB_trianLMER.5) # extracting the mean random intercept for each of trial variables

# plot the data with the predicted slopes overlayed
ggplot(PM_MB_train.2)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1,
               colour = c("Black",hue_pal()(10)))+
   coord_cartesian(ylim = c(0, 0.33))

Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha.` is set as a random slope to the random intercept `Trial_ref`.  
The model fits better as shown by an anova comparison. But how to impute from this model if mean variance for a trial is unknown....
```{r random_slope_model}
